---
title: "Matching Census Population to ACFRs Data at County Level"
author: "TN"
date: January 28, 2022
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(stringr)

```

# Census Population - County Level 

```{r}
d <- rio::import(here::here("data", "DECENNIALPL2020.P1_data_with_overlays_2021-12-16T123049.csv"), skip = 1) %>% 
  select(id, `Geographic Area Name`, `!!Total:`) %>% 
  rename(population = `!!Total:`)

# join with df_state to get state.abb and state.name --> to have a common col with acfrs to join
df_state <- data.frame(state.abb, state.name) %>% 
  add_row(state.abb = "PR", state.name = "Puerto Rico") %>% 
  add_row(state.abb = "DC", state.name = "District of Columbia")

pop <- d %>% 
  separate(`Geographic Area Name`, c("county", "state.name"), sep = ",")  %>%  
  mutate(state.name = str_trim(state.name)) %>% 
  left_join(df_state)

```

There are `r nrow(pop)` observations in census population data.


# ACFRs data - County Level

ACFRs data was queried from ACFRs PostgresQL database. The dataset was saved to R object `data_from_dbsite.RDS`. For security reason, the query commands are not included here.  

```{r}
acfrs <- readRDS("data_from_dbsite.RDS") %>% 
# rename to easily join with census data later
  rename(county = name) %>% 
  rename(state.abb = state)
acfrs

# Before: 31340 rows, when leaving out condition "NOT has_unconfirmed" --> get 33841 rows
```
ACFRs has `r nrow(acfrs)` observations. 

## Find "County" in ACFRs
```{r}
# ACFRs entities that contains the word "County" in their names
  acfrs_county <- acfrs %>% 
  filter(category == "General Purpose") %>% 
  filter(grepl("County", county))
  acfrs_county
```

There are `r nrow(acfrs_county)` entities that contain the word "county" in their names. 

## Louisiana

In Louisiana, counties are called Parishes.

```{r}

louisiana_parish <- acfrs %>% 
  filter(category == "General Purpose") %>%  
  filter(state.abb == "LA") %>% 
  filter(grepl("Parish", county))

```
There're `r nrow(louisiana_parish)` Louisiana entities that contain the word "Parish" in their names. 


## Alaska

Alaska often uses the term "Borough" instead of County. 
```{r}
#Check term “Municipality” too, not found any. 
alaska_borough <- acfrs %>% 
  filter(category == "General Purpose") %>%  
  filter(state.abb == "AK") %>% 
  filter(grepl("Borough", county)) %>% arrange(county)
```

Just to double check, find any ACFRs entities that has "Municipality" in their names.
```{r}
acfrs %>% filter(grepl("Municipality", county))

# Found 2: SD Municipality of Dell Rapids & WV Municipality of Parkersburg.
# However, they're not in Census population data
pop %>%
filter(county == "Municipality of Parkersburg" | county == "Municipality of Dell Rapids" )
          
```

### Puerto Rico (Note: not using to match with ACFRS for now)

Puerto Rico only has “Municipios” that perform the functions of both cities and counties.

The problem is: 
* In ACFRs, there's no Puerto Rico entities that has "Municipio" in their names.
* In Census, Puerto Rico counties do contain the word "Municipio" in their names.

Solution: Remove "Municipio" in the names in Census to match with ACFRs

Potential risk: Not all Puerto Rico entities in ACFRs without "Municipio" are actually a municipio.
```{r}
acfrs %>% 
  filter(category == "General Purpose") %>% 
  filter(state.abb == "PR") %>% 
  filter(grepl("Municipio", county))
```


```{r}
# in Census population, find county that has the word "Municipio" --> remove the word "Municipio" to match with acfrs 
puertorico_census_pop <- pop %>% 
          filter(state.name == "Puerto Rico") %>% 
  filter(grepl("Municipio", county)) %>% 
  mutate(county = str_remove(county, " Municipio")) 

# In ACFRs, get all PR entities in General Purpose 
 puertorico_afrs_census_pop <-  acfrs %>% 
          filter(category == "General Purpose") %>% 
          filter(state.abb == "PR") %>% 
  
#join Puerto Rico in acfrs with PR in census -
         left_join(puertorico_census_pop) %>% 
          drop_na(population) 
          
```


Update Feb 7/2022: Marc: "Drop Puerto Rico out of the county analysis?  I realize it
was in the 2020 Census data, but they are not going to be on our map."

# Join ACFRs and Census population data to get population for ACFRs counties 


Joining these components: 
* acfrs entities contain word "County" in their names
* acfrs entities of Louisiana that contain word "Parish" in their names
* Puerto Rico in acfrs and Census. Note that in ACFRs, there's no Puerto Rico entities has "Municipio". To match with PR in Census, need to remove this word from Census population data. This introduces a risk that there might be cases where PR entities in ACFRs without word "Municipio" are NOT actually Municipio.


```{r}
# first, join entities in ACFRs contain words "County" + Louisiana that contain word "Parish" + alaska that contain "Borough" in their names
acfrs_county_parish_borough <- rbind(acfrs_county, louisiana_parish) %>% rbind(alaska_borough)

# next, join with census Census population by = c("state.abb", "county")
county_pop_census_acfrs <- acfrs_county_parish_borough %>% 
            left_join(pop) %>% 
            drop_na(population) %>% 
            arrange(desc(population)) %>% distinct() 
  
# third, bind with puertorico - not using for now
           # rbind(puertorico_afrs_census_pop) 

write.csv(county_pop_census_acfrs, "county_pop_census_acfrs_TOTAL.csv")
saveRDS(county_pop_census_acfrs, "county_pop_census_acfrs.RDS")


```

The matched dataset has `r nrow(county_pop_census_acfrs)` observations/ counties. 

# List of counties in Census data with > 100k population  

```{r}
# stoplist

stoplist1 <-  pop %>% 
  filter(state.name == "New York" & county %in% c("Bronx County", "Richmond County", "Kings County", "Queens County", "New York County"))
  
stoplist2 <- pop %>% 
  filter(state.name == "Florida" & county == "Duval County") # FL Duval County's government is combined with FL Jacksonville,

stoplist3 <- pop %>% 
    filter(state.name == "Tennessee" & county == "Davidson County") 
    
stoplist4 <-  pop %>% 
  filter(state.name == "Kentucky" & county == "Jefferson County")

stoplist5 <- pop %>% 
    filter(state.name == "Ohio" & county == "Franklin County")
  
stoplist <- rbind(stoplist1, stoplist2, stoplist3, stoplist4, stoplist5)

# get counties in Census population data that have > 100k pop, county level, not Connecticut, not in stoplist

census_pop_100k <- pop %>% 
  # counties with > 100k  pop in Census
  filter(population > 100000) %>% 
  
  # only get county level 
  filter(grepl("County|Parish", county)) %>%  # how about |Borough?
  filter(state.name != "Connecticut") %>% 
  filter(!id %in% stoplist$id) 

```

## Counties in Census with > 100k population above that are not yet matched with ACFRs

```{r}
census_pop_NOT_match_acfrs_100k <- census_pop_100k %>% 
  filter(!id %in% county_pop_census_acfrs$id ) %>% arrange(desc(population)) %>% distinct()
#write.csv(census_pop_NOT_match_acfrs_100k, "census_pop_NOT_match_acfrs_100k.csv")
```

There are `r nrow(census_pop_NOT_match_acfrs_100k)` counties in Census with more than 100k population that are not yet matched with ACFRs. 

## All counties in Census, regardless of population size, that are not yet matched with ACFRs

county_pop_census_acfrs

```{r}
census_pop_NOT_match_acfrs_all <- pop %>% 

  # only get county level 
  filter(grepl("County|Parish", county)) %>%  # how about |Borough?
  filter(state.name != "Connecticut") %>%
  filter(!id %in% stoplist$id) %>% 
  filter(!id %in% county_pop_census_acfrs$id) %>% arrange(desc(population))

#write.csv(census_pop_NOT_match_acfrs_all, "census_pop_NOT_match_acfrs_all.csv")
```

There are `r nrow(census_pop_NOT_match_acfrs_all)` counties in Census, regardless of population size, that are not yet matched with ACFRs. 

```{r}
#++++++++
#Note: the below match is NOT accurate: it will filter out counties whose names appear in county_pop_census_acfrs. 
#Some states have counties with the same name. 
# Eg. this code will filter out "Kings County", both CA and NY. 
# WHile Kings County NY is not in ACFRs, Kings County CA is. 

#  filter(!county %in% county_pop_census_acfrs$county) %>% distinct()
#+++++++++
```

# County from 2017 Census

```{r}
acfrs %>% 
  filter(category == "General Purpose") %>% 
  filter(grepl("county|borough|parish", county, ignore.case = TRUE)) %>% arrange(county) -> t1

```


```{r}
#get sheet Marc created: "Data from CAFR System"
census2017 <- rio::import(here::here("data", "Mapping County Data from ACFR System to 2017 and 2020 Census.xlsx"), sheet = 3)

census2017 %>% 
  filter(grepl("county|borough|parish", Entity, ignore.case = TRUE)) %>% arrange(Entity) %>% 
  rename(state.abb = State, county = Entity) %>% 
  drop_na(`CAFR Year`) %>% # some rows have no years. Those with year 2020 are counties for which we have a CAFR for that year
  select(state.abb, county, `Census ID (from 2017)`) -> t2

# entities that are NOT in acfrs databse
entities_inCensus2017_NOT_inAcfrs <- t2 %>% left_join(t1) %>% # t1 has no NA in total_liabilities 
  filter(is.na(total_liabilities)) # after join, has these total_liabilities na => must be entities that are NOT in acfrs database. 

#write_csv(entities_inCensus2017_NOT_inAcfrs, "entities_inCensus2017_NOT_inAcfrs.csv")
```

