---
title: "Comparing Total_liability vs Sum of the components"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(writexl)
```

#### Read in data

```{r}
dec23 <- rio::import(here::here("data", "data-Dec23-2-tn.csv")) 

# data dimension 
dim(dec23)
```

The first few rows of the data

```{r}
head(dec23)
```

Summing up the following components to get column "sum_components": 
bonds_outstanding + compensated_absences + leases + loans_outstanding + net_pension_liability + net_opeb_liability.

Filter for rows that have sum_components - total_liabilities > 0

```{r}
dec23 %>% 
mutate(sum_components = (bonds_outstanding + compensated_absences + leases + loans_outstanding + 
                             net_pension_liability + net_opeb_liability)) %>% 
  mutate(sum_components_bigger = ifelse(sum_components - total_liabilities > 0, "Y", "N")) %>% 
  filter(sum_components_bigger == "Y") -> result2

result2 %>% head()
#write_xlsx(result2, "sum_component_bigger_total_liabilities.xlsx")
```

Result: there are `r nrow(result2)` cases where the sum of components bigger than total_liabilities 


#### Data Queried on December 23 using this: 
(Reuse Marc's code, cut off some fields & conditions)

select cafrs_state.abbreviation as state, cafrs_entity.name, cafrs_entity.category,

total_liabilities, bonds_outstanding, compensated_absences, leases, loans_outstanding, 

net_pension_liability,

net_opeb_liability

from cafrs_entity

inner join cafrs_state on (cafrs_entity.state_id = cafrs_state.id)

inner join cafrs_cafr on (cafrs_cafr.entity_id = cafrs_entity.id)

inner join cafrs_netposition on (cafrs_cafr.id = cafrs_netposition.cafr_id)

inner join cafrs_activities on (cafrs_cafr.id = cafrs_activities.cafr_id)

inner join cafrs_proprietaryrevenues on (cafrs_cafr.id = cafrs_proprietaryrevenues.cafr_id)

where category <> 'Non-Profit'

and cafrs_cafr.year = 2020

and not is_nonstandard

and is_valid

and reviewed_date is not null


