---
title: "State Government Vs. Component Units"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    toc_depth: 3
    
date: "2023-05-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(dplyr)
library(DT)
library(ggplot2)
library(forcats)
library(plotly)
```

### List of all 434 component units in 2020
```{r}
component_units2020 <- readRDS("data/data_from_dbsite_2020.RDS") %>% filter(!is.na(component_unit_of_id)) %>% select(state, name, total_liabilities, net_pension_liability)

component_units_bystate_2020 <- component_units2020 %>% 
  group_by(state) %>% 
  mutate(tot_component_units_liabilities = sum(total_liabilities),
         tot_component_units_netpension = sum(net_pension_liability)) %>% 
  select(state, tot_component_units_liabilities, tot_component_units_netpension) %>% distinct()

state_gov2020 <- readRDS("/Users/tn/Desktop/REASON/state_county_city/state_gov.RDS") %>% 
  select(state, total_liabilities, net_pension_liability)

component_units2021 <- readRDS("data/data_from_dbsite_2021.RDS") %>% filter(!is.na(component_unit_of_id))

component_units2020 %>% format(big.mark = ",") %>% datatable()

write.csv(component_units2020, "component_units2020.csv")
```

### State Government ACFRs vs. The Sum of Component Units by state ACFRs

pct_total_liabilities = sum of total liabilities of all component units / state government total_liabilities

pct_netpension = sum of net pension liabilities of all component units / state government net pension liabilities 


```{r}
state_gov2020 %>% left_join(component_units_bystate_2020) %>% 
  mutate(pct_total_liabilities = tot_component_units_liabilities/total_liabilities,
         pct_netpension = tot_component_units_netpension/net_pension_liability) %>% 
  arrange(desc(pct_total_liabilities)) -> dp2020

dp2020 %>% 
  format(big.mark = ",") %>% 
  datatable()

```

```{r}
dp2020 %>% 
  filter(!is.na(pct_total_liabilities)) %>% 
  ggplot(aes(fct_reorder(state, pct_total_liabilities), pct_total_liabilities)) +
  geom_col(fill = "lightblue") +
  coord_flip() +
  labs(title = "Total liabilities: \nThe sum of component units as a percentage of state government", 
       x = "") +
  theme_minimal() -> p1

ggplotly(p1)

```

### View component units of SC

```{r}
component_units2020 %>% filter(state == "SC") %>% 
  select(state, name, total_liabilities, net_pension_liability) %>% 
  arrange(desc(total_liabilities)) %>% 
  format(big.mark = ",") %>% 
  datatable()
```

### View component units of NY

```{r}
component_units2020 %>% filter(state == "NY") %>% 
  select(state, name, total_liabilities, net_pension_liability) %>% format(big.mark = ",") %>% 
  arrange(desc(total_liabilities)) %>% 
  datatable()
```

```{r}
dp2020 %>% 
  filter(!is.na(pct_netpension)) %>% 
  ggplot(aes(fct_reorder(state, pct_netpension), pct_netpension)) +
  geom_col(fill = "orange") +
  coord_flip() +
  labs(title = "Net Pension liabilities: \nThe sum of component units as a percentage of state government", 
       x = "") +
  theme_minimal() -> p2

ggplotly(p2)
```
### View component units of OK

```{r}
component_units2020 %>% filter(state == "OK") %>% 
  select(state, name, total_liabilities, net_pension_liability) %>% format(big.mark = ",") %>% 
  arrange(desc(total_liabilities)) %>% 
  datatable()
```
