---
title: "Matching ACFRs School Districts with NCES Student Enrollment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(stringr)
library(tidyr)
library(dplyr)

```

# Read in Data 


```{r nces_school_districts}
#data downloaded Jan 27, 2020. Not including charter schools. Student > 1. 
nces <- rio::import(here::here("data", "ncesdata_DBBFFFC.xlsx"), skip = 14) %>% 
  select(`NCES District ID`, `State District ID`, `District Name`, `County Name*`, City, State, `Students*`) %>% 
  rename(nces_original_name = `District Name`,
    county = `County Name*`, 
    state = State, 
    student = `Students*`) %>% 
  mutate(nces_name = str_to_lower(nces_original_name)) %>% drop_na(nces_name)
  
# acfrs from database, # only get School District

acfrs_school_districts <- readRDS("data_from_dbsite.RDS") %>% 
  rename(acfrs_original_name = name) %>% 
  filter(category == "School District") %>% 
  mutate(acfrs_name = str_to_lower(acfrs_original_name)) %>% drop_na(acfrs_name) 

```

# Example of 63 School Districts

This is a hand-matched example of 63 school district in NCES data & ACFRs. (Thank you! Marc)

Analyzing the pattern of match between these 2 datasets will help improving match in the full datasets. 

```{r}
example_match_60sd <- rio::import(here::here("data", "Mappings for Largest School Districts (2).xlsx")) %>% 
  rename(acfrs_name = `Name in ACFR System`, 
         nces_name = `District Name`) %>% 
  select(acfrs_name, nces_name, `State District ID`, `State...7`) 

example_match_60sd_clean <- example_match_60sd %>% 
   mutate(nces_name = str_to_lower(nces_name),
         acfrs_name = str_to_lower(acfrs_name)) %>% 
  
  # remove terms in acfrs, 1st time
  mutate(acfrs_name = str_remove_all(acfrs_name, "(the)?\\s*school district\\s*(of)?|county|independent school district|district school board|\\s*board of education\\s* (of the)?|public schools|the school board of|board of education|public school system")) %>% 

  # remove terms in acfrs, second time
  mutate(acfrs_name = str_trim(acfrs_name, side = "both")) %>% 
  mutate(acfrs_name = str_remove_all(acfrs_name, "^of\\s*|-$|municipalno.*|\\.|'s|’s|[0-9]*$")) %>% 
  mutate(acfrs_name = str_trim(acfrs_name, side = "both")) %>% # need to repeat b/c after removing words, space remains
  
  
  # remove terms in nces, 1st time
  mutate(nces_name = str_remove_all(nces_name, "(the)?\\s*school district\\s*(of)?|independent school district|district( school board)?|board of education|isd|public schools|schools|(co)? pblc schs|county|(city )?sd")) %>% 
  
  # remove terms in nces, 2nd time
  
  mutate(nces_name = str_trim(nces_name, side = "both")) %>% 
  mutate(nces_name = str_remove_all(nces_name, "^of\\s*|-$|municipalno.*|\\.|'s|’s|[0-9]*$")) %>% 
  mutate(nces_name = str_trim(nces_name, side = "both")) 
  

example_matched <- example_match_60sd_clean %>% 
  # check of the 2 name cols are identical
  mutate(same_name = ifelse(acfrs_name == nces_name, TRUE, FALSE)) %>% 
  filter(same_name == TRUE)

examples_NOT_matched <- example_match_60sd_clean %>% 
  # check of the 2 name cols are identical
  mutate(same_name = ifelse(acfrs_name == nces_name, TRUE, FALSE)) %>% 
  filter(same_name == FALSE)

```


# ACFRs data - School District

```{r}
options(scipen = 999)
acfrs_school_districts_clean <- acfrs_school_districts %>% 
  # remove terms in acfrs, 1st time
  mutate(acfrs_name = str_remove_all(acfrs_name, "(the)?\\s*school district\\s*(of)?|county|independent school district|district school board|\\s*board of education\\s* (of the)?|public schools|the school board of|board of education|public school system")) %>% 

  # remove terms in acfrs, second time
  mutate(acfrs_name = str_trim(acfrs_name, side = "both")) %>% 
  mutate(acfrs_name = str_remove_all(acfrs_name, "^of\\s*|-$|municipalno.*|\\.|'s|’s|[0-9]*$")) %>% 
  mutate(acfrs_name = str_trim(acfrs_name, side = "both")) %>%  arrange(acfrs_name) %>% 
  
  # use name to match with nces
  rename(name = acfrs_name) %>% 

  # some names got trimmed off using above regular expression, need to add back here. 
  mutate(name = ifelse(name == "" | name == "#", acfrs_original_name, name)) %>% 
  
   # change some names: "City of Chicago SD 299" in NCES is "Chicago Board of Education" in Acfrs 
  mutate(name = ifelse(acfrs_original_name == "Chicago Board of Education", "chicago board of education", name)) 

write_csv(acfrs_school_districts_clean, "acfrs_school_districts_clean.csv")
acfrs_school_districts_clean
```


# NOTE: unfunded liabilities school districts
nrow(acfrs_school_districts)
sum(acfrs_school_districts$net_pension_liability) 358944607669
sum(acfrs_school_districts$net_pension_assets) 2801641850

unfunded liabilities
358944607669 - 2801641850 = 356142965819

 unfunded liabilities ALL
sum(acfrs$net_pension_liability) 1671845182218
sum(acfrs$net_pension_assets) 12669982690
nrow(acfrs)
unfunded liabilities
1671845182218 - 12669982690 = 1,659,175,199,528

```{r}
nces_clean <- nces %>% select(-c(`State District ID`, City)) %>% 
  # remove terms in nces, 1st time
  mutate(nces_name = str_remove_all(nces_name, "(the)?\\s*school district\\s*(of)?|independent school district|district( school board)?|board of education|isd|public schools|schools|(co)? pblc schs|county|(city )?sd")) %>% 
  
  # remove terms in nces, 2nd time
  
  mutate(nces_name = str_trim(nces_name, side = "both")) %>% 
  mutate(nces_name = str_remove_all(nces_name, "^of\\s*|-$|municipalno.*|\\.|'s|’s|[0-9]*$")) %>% 
  mutate(nces_name = str_trim(nces_name, side = "both")) %>% arrange(nces_name) %>% slice(-c(1:1)) %>% rename(name = nces_name) %>% 

# Marc: "City of Chicago SD 299" in NCES is "Chicago Board of Education" in Acfrs 
mutate(name = ifelse(nces_original_name == "City of Chicago SD 299", "chicago board of education", name))
  
```

```{r}

matched_acfrs_nces_sd <- acfrs_school_districts_clean %>% 
  left_join(nces_clean) %>% 
  drop_na(student) %>%
  mutate(student = as.numeric(student)) %>% 
  arrange(desc(student)) %>% 
  select(-c(census_id, category, has_unconfirmed)) 

# write.csv(matched_acfrs_nces_sd, "matched_acfrs_nces_sd_withID.csv")
saveRDS(matched_acfrs_nces_sd, "matched_acfrs_nces_sd.RDS")

# include all, NOT drop_na
school_districts 
  
  acfrs_school_districts_clean %>% 
    left_join(nces_clean) %>% distinct(name) -> t1
  
  t1 %>% filter(!name %in% acfrs_school_districts_clean$name)
  
  acfrs_school_districts_clean %>% filter(!name %in% t1$name)
  
  t1 %>% 
    filter(name == "Independent School District 345")
  
  mutate(student = as.numeric(student)) %>% 
  arrange(desc(student)) %>% 
  select(-c(census_id, has_unconfirmed)) 

```




