---
title: "State and Local Government Liabilities Study"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, results = 'asis')
options(knitr.table.format = "html")
library(readxl)
library(tidyverse)
library(dplyr)
library(purrr)
library(kableExtra)
library(knitr)
library(DT)

```


```{r}

gdp_2020 <- readRDS("gdp_2020.RDS")

acfrs <- readRDS("data_from_dbsite.RDS")
d <- acfrs %>% 
  filter(category != "Non-Profit" & year == 2020) %>% 
  
  mutate("Liabilities/Revenues Ratio" = round(total_liabilities/(revenues + 1), 2),
         "Bonds Outstanding/Revenues Ratio" = round(bonds_outstanding/revenues, 2),
         "Net Pension Liability/Revenues Ratio" = round((net_pension_liability - net_pension_assets)/revenues, 2),
         "Net OPEB Liability/Revenues Ratio" = round((net_opeb_liability - net_opeb_assets)/revenues, 2), 
         "Compensated Absences/Revenues Ratio" = round(compensated_absences/revenues, 2), 
         "netted_net_pension_liability" = (net_pension_liability - net_pension_assets), 
         "netted_net_opeb_liability" = (net_opeb_liability - net_opeb_assets)) %>% 
  
  #rename for easier human read field names & table display
    rename(State = state,
         Entity = name,
         "Net Pension Liability" = net_pension_liability,
         "Net OPEB Assets" = net_opeb_assets,
         "Net OPEB Liability" = net_opeb_liability,
         "Bonds Outstanding" = bonds_outstanding,
         "Notes Outstanding" = notes_outstanding,
         "Leases" = leases,
         "Loans Outstanding" = loans_outstanding, 
         "Compensated Absences" = compensated_absences,
         "Total Liabilities" = total_liabilities,
         "Revenues" = revenues
         
         ) %>% 
  select(State, Entity, category, year, everything()) 

sum_tot_labilities <- round(sum(d$`Total Liabilities`)/1000000000000,2) #trillion

percent <- round(sum(d$`Total Liabilities`)/ (20893.75*1000000000)*100)
```

US state and local governments reported **$`r sum_tot_labilities` trillion** in liabilities in 2020, an amount that exceeds their annual revenue and is equal to *`r percent`%* of Gross Domestic Product. Reason Foundation computed this total and its subcomponents by reviewing 30,000 audited government financial statements filed by state and local governments for their 2020 fiscal year.

The state and local governments that reported the largest liabilities were as follows:

```{r, results='asis', include=FALSE}
individual_fields <- c("Bonds Outstanding", "Net Pension Liability", "Net OPEB Liability", "Compensated Absences", "Total Liabilities")

get_field_value <- function (field) {
  
  df <- d %>%
  select(State, Entity, all_of(field))

df %>% 
  arrange(desc(df[3])) %>% 
  head(10) -> d1 

knitr::kable(d1, 
      #caption = (d1 %>% colnames())[3], row.names = FALSE,
      align = c('l', 'l', 'r'),
      format.args = list(big.mark = ",")) %>% 
    # kable_paper("striped") %>% 
      row_spec(row = 0, background =  "#FF6C30", color = "white", bold = TRUE) %>% 
  kable_styling(full_width = TRUE) -> result 

print(result)
cat('\n')
  
}

```


```{r, fig.width= 10, fig.height=10, out.width=50}
get_field_value("Total Liabilities")
```







