---
title: "Some visualization of Cities"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(results = 'asis', echo = FALSE, warning = FALSE, message = FALSE)
options(scipen = 999)
library(tidyverse)
library(dplyr)
library(purrr)
library(knitr)
library(DT)
library(ggrepel)
#acfrs_city_pop_added_char <- readRDS("acfrs_city_pop_added_char.RDS")
# probelem with integer64
acfrs_city_pop_added_char <- rio::import(here::here("acfrs_city_pop_added_char.csv"))
```


# Total Liabilities 
## Cities with Population < 1 Mil

```{r}

  acfrs_city_pop_added_char %>% 
    drop_na(total_liabilities) %>% 
  filter(population > 1000 & population < 1000000 &
           total_liabilities > 0)  %>% 
  select(population, name, total_liabilities, revenues) %>% 
  mutate(
    tot_liabilities_mil = round(total_liabilities/1000000),
         tot_revenues_mil = round(revenues/1000000)) -> d1
```

```{r}
  d1 %>% 
  ggplot(aes(population, tot_liabilities_mil)) +
  geom_point(color = "#8EA0CB", alpha = .5) +
  
    # add lines 
  geom_hline(yintercept = round(mean(d1$tot_liabilities_mil)),
             linetype = "dashed", color = "red", size = .5) +
    annotate(geom = "text", x = 600000, y = 200, label = paste("Mean = ", round(mean(d1$tot_liabilities_mil)))) +
    
    
 geom_hline(yintercept = round(median(d1$tot_liabilities_mil)),
           linetype = "dashed", color = "blue", size = .5) +
    annotate(geom = "text", x = 600000, y = 20, label = paste("Median = ", round(median(d1$tot_liabilities_mil)))) +
    
  scale_x_log10() + 
  scale_y_log10() +
  labs(
    x = "Population (log scale)",
    y = "Million USD (log scale)",
    title = "Total Liabilities by population among the cities",
    subtitle = "1000 < Population < 1000000") +
  theme_minimal()
```
  
## Cities with Population > 1 Mil  

```{r, results= 'asis'}

  acfrs_city_pop_added_char %>% 
    select(population, name, total_liabilities, revenues) %>% 
    filter(population > 1000000) %>% 
    mutate(tot_liabilities_mil = round(total_liabilities/1000000),
         tot_revenues_mil = round(revenues/1000000),
         population_mil = population/1000000) -> d2 
  
  d2 %>%   
  ggplot(aes(population_mil, tot_liabilities_mil)) +
  geom_point(color = "#8EA0CB", alpha = .8, size = 4) +
    
  geom_text_repel(aes(label = name), nudge_y = 0.1, nudge_x = 0.1, segment.curvature = -0.1) +
  
  geom_hline(yintercept = round(mean(d2$tot_liabilities_mil)),
             linetype = "dashed", color = "red", size = .5) +
annotate(geom = "text", x = 7, y = 40000, label = paste("Mean = ", round(mean(d2$tot_liabilities_mil)))) +
  
 geom_hline(yintercept = round(median(d2$tot_liabilities_mil)),
           linetype = "dashed", color = "blue", size = .5) +
annotate(geom = "text", x = 7, y = 15000, label = paste("Median = ", round(median(d2$tot_liabilities_mil)))) +
    
  scale_x_log10() + 
  scale_y_log10() +
  labs(
    x = "Population in Million (log scale))",
    y = "Million USD (log scale)",
    title = "Total Liabilities by population in 10 cities",
    subtitle = "Population > 1000000"
  ) +
  theme_minimal()
```

# Total Revenues 
## Cities with population < 1 Mil

```{r}
d1 %>% 
  ggplot(aes(population, tot_revenues_mil)) +
  geom_point(color = "#A6D753", alpha = .3) +
  
  geom_hline(yintercept = round(mean(d1$tot_revenues_mil)),
             linetype = "dashed", color = "red", size = .5) +
  annotate(geom = "text", x = 600000, y = 100, label = paste("Mean = ", round(mean(d1$tot_revenues_mil)))) +
  
 geom_hline(yintercept = round(median(d1$tot_revenues_mil)),
           linetype = "dashed", color = "blue", size = .5) +
 annotate(geom = "text", x = 600000, y = 20, label = paste("Median = ", round(median(d1$tot_revenues_mil)))) +
  
  scale_x_log10() + 
  scale_y_log10() +
  labs(
    x = "Population (log scale)",
    y = "Million USD (log scale)",
    title = "Total Revenues by population among the cities",
    subtitle = " 1000 < Population < 1 Million"
  ) +
  theme_minimal()
```

## Cities with population > 1 Mil
```{r}

d2 %>%   
  ggplot(aes(population_mil, tot_revenues_mil)) +
  geom_point(color = "#A6D753", alpha = .8, size = 4) +
    
  geom_text_repel(aes(label = name), nudge_y = 0.1, nudge_x = 0.1, segment.curvature = -0.1) +
  
  geom_hline(yintercept = round(mean(d2$tot_revenues_mil)),
             linetype = "dashed", color = "red", size = .5) +
annotate(geom = "text", x = 7, y = 14000, label = paste("Mean = ", round(mean(d2$tot_revenues_mil)))) +
  
 geom_hline(yintercept = round(median(d2$tot_revenues_mil)),
           linetype = "dashed", color = "blue", size = .5) +
  annotate(geom = "text", x = 7, y = 5200, label = paste("Median = ", round(median(d2$tot_revenues_mil)))) +
  scale_x_log10() + 
  scale_y_log10() +
  labs(
    x = "Population in Million (log scale)",
    y = "Million USD (log scale)",
    title = "Total Revenue by population in 10 cities",
    subtitle = "Population > 1000000"
  ) +
  theme_minimal()
```

# Six biggest city governments

```{r}

acfrs_city_pop_added_char %>% 
 #arrange(desc(population)) %>% slice(1:6) # find 6 largest cities
  #filter(name == "Phoenix")
  filter(name %in% c("New York City", "Los Angeles", "Chicago", "Houston", "Philadelphia", "Phoenix") & !state.abb %in% c("TN", "OR")) %>% 
  datatable(fillContainer = FALSE, 
            options = list(pageLength = 5))
```

# Total revenues and Total Liabitity per person

```{r, results= 'asis', include=FALSE}

acfrs_city_pop_added_char %>% 
  filter(name %in% c("New York City", "Los Angeles", "Chicago", "Houston", "Phoenix", "Philadelphia") & !state.abb %in% c("TN", "OR")) %>% # Philadelphia of PA, not TN; Phoenix of AZ, not OR
 select(name, total_liabilities, state.abb, revenues, population) %>%

  #normalize total_liabilities and revenues by mil population / or by each person
  mutate(liability_person = round(total_liabilities/population)) %>%
  mutate(revenues_person = round(revenues/population)) -> top6_cities


top6_cities %>%
  pivot_longer(cols = 6:7,
               names_to = "type",
               values_to = "Value") %>%
  # mutate(total_liabilities = bit64::as.integer64(total_liabilities),
  #        revenues = bit64::as.integer64(revenues), 
  #        value = bit64::as.integer64(value)) %>% 
  select(name, type, Value) -> dp

```


## Total revenues and Total Liabitity per person in 6 largest cities

```{r, echo=FALSE}
dp %>% 
ggplot(aes(name, Value, fill = type)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = Value), 
            position = position_dodge(0.9), vjust = 0) + #give the labels the virtual with
  
  scale_fill_manual(values = c("#8EA0CB", "#A6D753" )) +

  labs(
    x = "",
    y = "USD (raw scale)",
    title = "Total revenues and Total Liabitity per person in 6 largest cities"
  ) +
        
 guides(fill = guide_legend(title = NULL)) +
 theme_minimal()

```
## Total revenues and Total Liabitity per person in 6 largest cities - Comparison 
```{r, results= 'asis', echo=FALSE}
top6_cities %>%
  pivot_longer(cols = 6:7,
               names_to = "type",
               values_to = "Value") %>%
ggplot(aes(name, Value, fill = type)) +
  
 
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = Value), 
            position = position_dodge(0.9), vjust = 0) + #give the labels the virtual with
  
   #average liabilities per person of all cities
geom_hline(yintercept = round(mean(acfrs_city_pop_added_char$total_liabilities/ acfrs_city_pop_added_char$population)),
           linetype = "dashed", color = "#8EA0CB", size = 1) +
  
  #average revenues per person of all cities
geom_hline(yintercept = round(mean(acfrs_city_pop_added_char$revenues/ acfrs_city_pop_added_char$population)),
           linetype = "dashed", color = "#A6D753", size = 1) +
  
  scale_fill_manual(values = c("#8EA0CB", "#A6D753" )) +

  labs(
    x = "",
    y = "USD (raw scale)",
    title = "Total revenues and Total Liabitity per person in 6 largest cities\nComparison with average values per person of all cities",

  ) +
        
 guides(fill = guide_legend(title = NULL)) +
 theme_minimal()

```


```{r}
# State governments
# 
# Similarly, please send a sheet showing the data categories/columns that all state governments could be compared across by using big states like California, Texas, Florida, and New York to give us examples. 
```

